Lossy compression of DNA sequencing quality data

### 2015-05-04 manuscript/q-compression.tex
Added back multi-bin encoding.  Updated preprocessing figure and author list.

\title[lossy-compression]{Lossy compression of DNA sequencing quality
  data} \author[El Hadidi \textit{et~al.}]{Mohamed El
  Hadidi\,$^{1}$\footnote{authors contributed equally}, Christopher
  M. Hill\,$^{2}$\footnotemark[1], Andr\'{a}s
  Szolek\,$^{3}$\footnotemark[1], and Michael
  P. Cummings\,$^4$\footnote{to whom correspondence should be
    addressed}} \address{$^{1}$Department of Algorithms in
  Bioinformatics, Center for Bioinformatics, University of
  T\"{u}bingen, Sand 14, 72076 T\"{u}bingen, Germany
  \\ $^{2}$Department of Computer Science, University of Maryland,
  College Park, Maryland, 20742 USA\\ $^{3}$Department of Applied
  Bioinformatics, Center for Bioinformatics, Quantitative Biology
  Center, and Department of Computer Science, University of
  T\"{u}bingen, Sand 14, 72076 T\"{u}bingen, Germany\\ $^{4}$Center
  for Bioinformatics and Computational Biology, University of
  Maryland, College Park, Maryland, 20742 USA}
\history{Received on XXXXX; revised on XXXXX; accepted on XXXX}
\editor{Associate Editor: XXXXXXX}

@@

>>>>

\title[lossy-compression]{Lossy compression of DNA sequencing quality
  data} \author[Hill \textit{et~al.}]{Christopher
  M. Hill\,$^{1}$, Andr\'{a}s Szolek\,$^{2}$, Mohamed El
  Hadidi\,$^{3}$, and Michael P. Cummings\,$^4$\footnote{to whom correspondence should be
    addressed}} \address{$^{1}$Department of Computer Science, University of Maryland,
  College Park, Maryland, 20742 USA\\ $^{2}$Department of Applied
  Bioinformatics, Center for Bioinformatics, Quantitative Biology
  Center, and Department of Computer Science, University of
  T\"{u}bingen, Sand 14, 72076 T\"{u}bingen, Germany\\ 
  $^{3}$Department of Algorithms in
  Bioinformatics, Center for Bioinformatics, University of
  T\"{u}bingen, Sand 14, 72076 T\"{u}bingen, Germany
  \\ $^{4}$ Center for Bioinformatics and Computational Biology, University of
  Maryland, College Park, Maryland, 20742 USA}
\history{Received on XXXXX; revised on XXXXX; accepted on XXXX}
\editor{Associate Editor: XXXXXXX}

@@

While we focus only on two bins in this work, a greater number of bins can be used in practice. For example, an additional third bin (\emph{okay}) can be used for base qualities near the border between bins in the 2-bin encoding.  Examining the trade-off of additional bins and their resulting compressibility and affect on downstream analyses is outside the scope of this work.
